\documentclass[12pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{amsfonts,amsmath}

% Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\title{Security 1 - Mandatory Hand-in 2}
\date{\today}
\author{Sam Al-Sapti (sals@itu.dk)}


\begin{document}
    \maketitle

    \section*{Part 1}

    To solve the problem at hand, the following protocol can be used:

    \begin{enumerate}
        \item Alice and Bob agree on a cyclic group $(\mathbb{Z}^*_p, \cdot)$
        with generators $g$ and $h$.
        \item Using Pedersen commitments, Alice samples a random $r \in
        \mathbb{Z}^*_p$ and a die throw $m$, and sends commitment $c = C(m, r)$ to
        Bob.
        \item Bob sends a die throw $t$ to Alice.
        \item Alice sends $(m, r)$ to Bob, who then verifies that $c = C(m, r)$.
        \item Alice and Bob each compute the final value $m \text{ XOR } t$.
    \end{enumerate}

    To ensure confidentiality, integrity and authenticity, a secure channel is
    established with mutual TLS (mTLS), meaning that both communicating parties
    authenticate themselves with certificates. For the purposes of this
    assignment, I will be using self-signed certificates instead of signing
    them by a certificate authority (CA).

    \section*{Part 2}

    TLS is used as a key exchange protocol to obtain a shared symmetric key for
    encryption. This is to ensure confidentiality. Furthermore, with mTLS, both
    parties authenticate themselves with their personal certificates. This part
    ensures authenticity from both sides. Lastly, as part of the TLS protocol,
    each message is sent along with a message authentication code (MAC). This
    ensures integrity. It also ensures authenticity, as only the parties
    participating in the key exchange will be able to create the MACs.
    
    The commitments ensure that no party can cheat with their die throw. Each
    party can send their die throw without first learning the other party's
    throw, such that no party has any influence on the final result.

\end{document}
